---
title: "Test-Function-AF"
format: html
---

## Set things up
```{r}
rm(list = ls())
library(tidyverse)
library(here)
```

Here is where I am going to test different functions that will help me to figure out how to make the final function

I will use some more simplistic functions and stuff to test these

## First Function:

```{r}
combine_csv <- function(path){
  # create a list of all the csv files in the given directory
  # use list.files() and make it recursive to go through sub-directories
  # \\.csv$ looks for files with the .csv at the end of the file path
  csv_list <- list.files(path = path, recursive = TRUE, pattern = "\\.csv$", full.names = TRUE) |> 
    lapply(read.csv) |>  # read in all the csvs
    bind_rows() # this appends all the dataframes
  return(csv_list) 
}
```


## Data

dummy "data" directory and some csv files for testing:

```{r}
dir.create("temp")
dir.create("temp/baggie")
dir.create("temp/case")

# baggie folder
dir.create("temp/baggie/A004_SD001")
# A004_SD001 subfolder
dir.create("temp/baggie/A004_SD001/20251214")

# case folder
dir.create("temp/case/A005_SD020")
dir.create("temp/case/A006_SD021")
# A005_SD020 subfolder
dir.create("temp/case/A005_SD020/20250607")

write.csv(data.frame(a = 1:3, b = 4:6), "temp/file1.csv")
write.csv(data.frame(a = 7:9, b = 10:12), "temp/baggie/A004_SD001/20251214/file2.csv")
write.csv(data.frame(a = 10:12, b = 13:15), "temp/case/A005_SD020/20250607/file3.csv")
file.create("temp/case/A005_SD020/file4.txt")
```

## Delete Data

```{r}
unlink("temp", recursive = T)
```


Testing some code that can be added to the function

```{r}
csv_list <- list.files(path= here("Code", "temp"), full.names = T, recursive = T, pattern = "\\.csv$")
csv_list

dframe <- lapply(csv_list, read.csv)  |>  
  bind_rows() 
dframe

```





Test the function:

```{r}
test <- combine_csv(here("Code", "temp"))
test
unlink("temp", recursive = T)
```

Ok that worked, but now we want to get rid of the X column and to add a variable that adds the sub directory into a column

This will allow the baggie and no baggie groups to have binary variable for analysis

Let's look at how a loop could potentially select for .csv files only within the baggie or case folders (before writing the function):

## Loop

```{r}
# make sure you have ran temp directory code chunk before running this code!!!!
# create an empty vector that will hold the desired files
final_list <- c()

# create an empty vector that will hold the list of "baggie or case" that will turn into one of the variables
bag_case <- c()

# create an empty vector that will hold the name of the AM

AM <-  c()

# Lets get a list of all the .csvs first:
csv_list <- list.files(path= here("Code", "temp"), full.names = T, recursive = T, pattern = "\\.csv$")
csv_list

# this is to check the loop that I will put into the function
for(i in csv_list){
  if(str_detect(i, "/baggie/")){
    final_list <- c(final_list, i)
    bag_case <- c(bag_case, "baggie")
    AM <- c(AM, basename(dirname(dirname(i))))
  } else if (str_detect(i, "/case/")){
    final_list <- c(final_list, i)
    bag_case <- c(bag_case, "case")
    AM <- c(AM, basename(dirname(dirname(i))))
  }
}

final_list
bag_case
AM

```

## Trying different loop:

```{r}
baggie_list <- list()

csv_list <- list.files(path= here("Code", "temp"), full.names = T, recursive = T, pattern = "\\.csv$")
csv_list

for(i in csv_list){
  if(str_detect(i, "/baggie/")){ 
    b_df <- read.csv(i)
    # find the AM from the path and add it as a column with the ID filled in
    AM <- dirname(i) |> dirname() |> basename()
    b_df$AM_ID <- rep(AM, nrow(b_df))
    
    # Same here but using the folder name and converting it to a date
    date <- dirname(i) |> basename() |> ymd()
    b_df$date <- rep(date, nrow(b_df))
    
    # update the list containing all the baggie AM data frames
    baggie_list <- c(baggie_list, b_df)
  }
}
  
dframe <-   bind_rows(baggie_list)
dframe
```


This loop works now I can add it to the function!

## Final Function

Also I want to require that tidyverse is loaded and add in a date column

Possibly return the dataframe and write the csv

```{r}
AM_baggie_csv <- function(path, csv = F, csv_name = "baggie_test.csv"){
  
# This function takes the output (CSVs) from BirdNet from 'baggie test' audio moth test and combines them into one data frame
# It also allows for a 'master' CSV to be written as part of the function as well, but for directly using the function in R there is no need to write the csv, so that's why it is a Boolean value
# NOTE: This function is highly specific to the BirdNet output and the workflow we are using.
# There is definitely a more general version of this function if need be
  
# start with making sure that tidyverse is turned on
require(tidyverse)
  
# create an empty list that will hold the all the baggie files
baggie_list <- list()

# create an empty list that will hold the all the case files
case_list <- list()

# Lets get a list of all the .csvs first:
csv_list <- list.files(path = path, full.names = T, recursive = T, pattern = "\\.csv$")

# This loop checks if the a csv file is in either the baggie or case folder and adds it to each respective list
for(i in csv_list){
  if(nrow(read.csv(i)) == 0)
    next
  else if(str_detect(i, "/baggie/")){ 
    b_df <- read.csv(i)
    # find the AM from the path and add it as a column with the ID filled in
    AM_b <- dirname(i) |> dirname() |> basename()
    b_df$AM_ID <- rep(AM_b, nrow(b_df))
    
    # Same here but using the folder name and converting it to a date
    date_b <- dirname(i) |> basename() |> ymd()
    b_df$date <- rep(date_b, nrow(b_df))
    
    # update the list containing all the baggie AM data frames
    # list() wraps the new dataframe as a new element in the list
    baggie_list <- c(baggie_list, list(b_df)) 
    
  } else if (str_detect(i, "/case/")){
    c_df <- read.csv(i)
    # find the AM from the path and add it as a column with the ID filled in
    AM_c <- dirname(i) |> dirname() |> basename()
    c_df$AM_ID <- rep(AM_c, nrow(c_df))
    
    # Same here but using the folder name and converting it to a date
    date_c <- dirname(i) |> basename() |> ymd()
    c_df$date <- rep(date_c, nrow(c_df))
    
    # update the list containing all the baggie AM data frames
    case_list <- c(case_list, list(c_df)) 
    
  }
}


# Read in the baggie list
baggie_df <- bind_rows(baggie_list)

# Fill in "baggie" for all the values in the housing column
baggie_df$housing <- rep("baggie", nrow(baggie_df))

# Read in the case list
case_df <- bind_rows(case_list)

#Fill in "case for all the values in the housing column
case_df$housing <- rep("case", nrow(case_df))

# Merge the two dataframes
dframe <- bind_rows(baggie_df, case_df)

# Remove the 'X' column
dframe$X <- NULL

# Now check if we want to write the csv
if(csv == T){
  write.csv(dframe, csv_name)
}
  
  return(dframe)
}
```


Let's check if it works!

## Test Final Function

```{r}
AM_baggie_csv(here("Code", "temp"))
```

#### Test with real data

```{r}
AM_baggie_csv(here("baggie_test_dummy"))
```

Its not working with a sample of our actual data:

Here I added some code to check if the file was empty and to wrap the addition to the list so that each data frame actually becomes a new element in the list.

```{r}
# create an empty list that will hold the all the baggie files
baggie_list <- list()

# create an empty list that will hold the all the case files
case_list <- list()

# Lets get a list of all the .csvs first:
csv_list <- list.files(path = here("baggie_test_dummy"), full.names = T, recursive = T, pattern = "\\.csv$")

# This loop checks if the a csv file is in either the baggie or case folder and adds it to each respective list
for(i in csv_list){
  # this checks if the data file is empty and if so moves to the next file
  if(nrow(read.csv(i)) == 0)
    next
  else if(str_detect(i, "/baggie/")){ 
    b_df <- read.csv(i)
    # find the AM from the path and add it as a column with the ID filled in
    AM_b <- dirname(i) |> dirname() |> basename()
    b_df$AM_ID <- rep(AM_b, nrow(b_df))
    
    # Same here but using the folder name and converting it to a date
    date_b <- dirname(i) |> basename() |> ymd()
    b_df$date <- rep(date_b, nrow(b_df))
    
    # update the list containing all the baggie AM data frames
    # list() wraps the next entry so that it becomes a new element in the list
    baggie_list <- c(baggie_list, list(b_df))
    
  } else if (str_detect(i, "/case/")){
    c_df <- read.csv(i)
    # find the AM from the path and add it as a column with the ID filled in
    AM_c <- dirname(i) |> dirname() |> basename()
    c_df$AM_ID <- rep(AM_c, nrow(c_df))
    
    # Same here but using the folder name and converting it to a date
    date_c <- dirname(i) |> basename() |> ymd()
    c_df$date <- rep(date_c, nrow(c_df))
    
    # update the list containing all the baggie AM data frames
    case_list <- c(case_list, list(c_df))
    
  }
}


#baggie_list

# Read in the baggie list
baggie_df <- bind_rows(baggie_list)
baggie_df
```





